---
title: "HW1"
author: "Zhengyu Lu"
date: '2022-09-12'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### (a) Which of the predictors are quantitative, and which are qualitative?

```{r}
Auto <- read.csv("Auto.csv", na.strings = "?",
                 stringsAsFactors = T)
Auto <- na.omit(Auto)
str(Auto)
```
I think "name" and "origin" are qualitiative, the other variables are quantitative

### (b) What is the range of each quantitative predictor? You can answerthis using the range() function.

```{r}
range(Auto$mpg)
range(Auto$cylinders)
range(Auto$displacement)
range(Auto$horsepower)
range(Auto$weight)
range(Auto$acceleration)
range(Auto$year)
```
### (c)What is the mean and standard deviation of each quantitative predictor?
#### mean
```{r}
summary(Auto[,1:7])
```
#### standard deivation
```{r}
sd(Auto$mpg)
sd(Auto$cylinders)
sd(Auto$displacement)
sd(Auto$horsepower)
sd(Auto$weight)
sd(Auto$acceleration)
sd(Auto$year)
```

### (d) Now remove the 10th through 85th observations. What is the range, mean, and standard deviation of each predictor in the subset of the data that remains? 
#### remove
```{r}
subset<- Auto[-c(10:85),(1:8)]
```
#### range
```{r}
range(subset$mpg)
range(subset$cylinders)
range(subset$displacement)
range(subset$horsepower)
range(subset$weight)
range(subset$acceleration)
range(subset$year)
range(subset$origin)
```
#### mean
```{r}
summary(subset)
```
#### standard deviation
```{r}
sd(subset$mpg)
sd(subset$cylinders)
sd(subset$displacement)
sd(subset$horsepower)
sd(subset$weight)
sd(subset$acceleration)
sd(subset$year)
sd(subset$origin)
```
### (e) Using the full data set, investigate the predictors graphically, using scatterplots or other tools of your choice. Create some plots highlighting the relationships
```{r}
pairs(Auto)
```

As the scatterplots show, there are some obvious linear and non-linear relationships among the predictors. For example, mpg and horsepower have a non-linear relationship, mpg decreases as horsepower increases; Displacement and weight have a nearly linear relationship, displacement increases as weight increases.

### Suppose that we wish to predict gas mileage (mpg) on the basis of the other variables. Do your plots suggest that any of the other variables might be useful in predicting mpg? Justify your answer.

As the scatterplots show, cylinders, horsepower, year, origin might be useful in predicting mpg because they have obvious linear and non-linear relationships. Cylinders=4 tend to have higher mpg, Japanese cars (origin=3) tend to have higher mpg than US and European cars, mpg increase as the year increase but mpg decrease as the horsepower increase.

